Relational Parametricity for Algebraically Indexed Types

### 2012-05-29 paper/section-general-framework.tex
Fixes to some formatting, and change of '=' to \isDefinedAs, where appropriate

For each primitive type $\tyPrimNm{X} \in \PrimTypeSet$, we assume
that $\tyPrimNm{X}$ is assigned a set $\tyPrimSem{\tyPrimNm{X}}$. We
extend this to assign a set to every well-formed type by induction on
the type structure by the following clauses.
\begin{displaymath}
  \begin{array}{cc}
    \begin{array}{l}
      \tySem{\tyUnit} \isDefinedAs \{*\} \\
      \tySem{A \tyProduct B} \isDefinedAs \tySem{A} \times \tySem{B} \\
      \tySem{A \tyArr B} \isDefinedAs \tySem{A} \to \tySem{B} \\
    \end{array}
    &
    \begin{array}{l}
      \tySem{A + B} \isDefinedAs \tySem{A} + \tySem{B} \\
      \tySem{\tyPrim{X}{e_1,...,e_n}} \isDefinedAs \tyPrimSem{\tyPrimNm{X}} \\
      \tySem{\forall i\mathord:s. A} \isDefinedAs \tySem{A}
    \end{array}
  \end{array}
\end{displaymath}
The interpretation of the unit type is a chosen one element set, and
the interpretations of the function, tuple and sum types is simply by
the corresponding construction on sets. The interpretation of the
universal quantifier simply ignores the indexing: the interpretation
of the type $\forall i\mathord:s.A$ is exactly the interpretation of
the type $A$.

\begin{example}[Units of Measure] Kennedy's original units of measure
  system seen as an instantiation of our system uses the assignment
  $\tyPrimSem{\mathsf{unit}} = \mathbb{Q}$, where $\mathbb{Q}$ is the
  set of rational numbers.
\end{example}

@@

\begin{example}[Units of Measure]
  FIXME: give two examples of relational environments.
\end{example}

Given a relation environment $\rho \in \relEnv{E}(\Delta)$, we define
the set of extensions $\extends{\rho}{i\mathord:s}$ of $\rho$ by an
additional index variable $i\mathord:s$ to be the following:
\begin{displaymath}
  \extends{\rho}{i\mathord:s} = \{ \rho' \in \relEnv{E}(\Delta,i\mathord:s) \sepbar \rho' \circ \pi^*_{i\mathord:s} = \rho \}
\end{displaymath}

>>>>

For each primitive type $\tyPrimNm{X} \in \PrimTypeSet$, we assume
that $\tyPrimNm{X}$ is assigned a set $\tyPrimSem{\tyPrimNm{X}}$. We
extend this to assign a set to every well-formed type by induction on
the type structure by the following clauses.
\begin{displaymath}
  \begin{array}{@{\hspace{0.2em}}c@{\hspace{0em}}c}
    \begin{array}{l}
      \tySem{\tyUnit} \isDefinedAs \{*\} \\
      \tySem{A \tyProduct B} \isDefinedAs \tySem{A} \times \tySem{B} \\
      \tySem{A \tyArr B} \isDefinedAs \tySem{A} \to \tySem{B} \\
    \end{array}
    &
    \begin{array}{l}
      \tySem{A + B} \isDefinedAs \tySem{A} + \tySem{B} \\
      \tySem{\tyPrim{X}{e_1,...,e_n}} \isDefinedAs \tyPrimSem{\tyPrimNm{X}} \\
      \tySem{\forall i\mathord:s. A} \isDefinedAs \tySem{A}
    \end{array}
  \end{array}
\end{displaymath}
The interpretation of the unit type is a chosen one element set, and
the interpretations of the function, tuple and sum types is simply by
the corresponding construction on sets. The interpretation of the
universal quantifier simply ignores the indexing: the interpretation
of the type $\forall i\mathord:s.A$ is exactly the interpretation of
the type $A$.

\begin{example}[Units of Measure] Kennedy's original units of measure
  system seen as an instantiation of our system uses the assignment
  $\tyPrimSem{\mathsf{unit}} \isDefinedAs \mathbb{Q}$, where
  $\mathbb{Q}$ is the set of rational numbers.
\end{example}

@@

\begin{example}[Units of Measure]
  FIXME: give two examples of sets of relational environments.
\end{example}

% FIXME: motivate this in terms of the semantics of forall types
Given a relation environment $\rho \in \relEnv{E}(\Delta)$, we define
the set of extensions $\extends{\rho}{i\mathord:s}$ of $\rho$ by an
additional index variable $i\mathord:s$ to be the following:
\begin{displaymath}
  \extends{\rho}{i\mathord:s} \isDefinedAs \{ \rho' \in \relEnv{E}(\Delta,i\mathord:s) \sepbar \rho' \circ \pi^*_{i\mathord:s} = \rho \}
\end{displaymath}
